Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-20 hpmoon-asoco.tex
Added bbl to the tex to set new references in blue

\bibliographystyle{elsarticle-num}
\bibliography{hpmoon-asoco}

>>>>

%\bibliographystyle{elsarticle-num}
%\bibliography{hpmoon-asoco}
\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{Gong15models}
Y.~Gong, W.~Chen, Z.~Zhan, J.~Zhang, Y.~Li, Q.~Zhang, J.~Li, Distributed
  evolutionary algorithms and their models: {A} survey of the state-of-the-art,
  Appl. Soft Comput. 34 (2015) 286--300.

\bibitem{Alba02Parallelism}
E.~Alba, M.~Tomassini, Parallelism and evolutionary algorithms, {IEEE} Trans.
  Evolutionary Computation 6~(5) (2002) 443--462.

\bibitem{Mora13paretobased}
A.~M. Mora, P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~J. Merelo-Guerv{\'{o}}s, P.~A.
  Castillo, Pareto-based multi-colony multi-objective ant colony optimization
  algorithms: an island model proposal, Soft Comput. 17~(7) (2013) 1175--1207.

\bibitem{LIU2017344}
Y.~Liu, D.~Gong, X.~Sun, Y.~Zhang, Many-objective evolutionary optimization
  based on reference points, Appl. Soft Comput. 50 (2017) 344 -- 355.

\bibitem{Luna15Survey}
F.~Luna, E.~Alba, Parallel multiobjective evolutionary algorithms, in:
  J.~Kacprzyk, W.~Pedrycz (Eds.), Springer Handbook of Computational
  Intelligence, Springer, 2015, pp. 1017--1031.

\bibitem{Mukhopadhyay14Survey}
A.~Mukhopadhyay, U.~Maulik, S.~Bandyopadhyay, C.~A.~C. Coello, A survey of
  multiobjective evolutionary algorithms for data mining: Part {I}, {IEEE} T.
  Evolut. Comput. 18~(1) (2014) 4--19.

\bibitem{Chavez15MO}
F.~C. de~la O, E.~Clemente, D.~E. Hern{\'{a}}ndez, F.~F. de~Vega, G.~Olague, A
  multi-objective evolutionary algorithm for interaction systems based on laser
  pointers, in: A.~M. Mora, G.~Squillero (Eds.), Applications of Evolutionary
  Computation - 18th European Conference, EvoApplications 2015, Copenhagen,
  Denmark, April 8-10, 2015, Proceedings, Vol. 9028 of Lecture Notes in
  Computer Science, Springer, 2015, pp. 504--516.

\bibitem{Hidalgo16residualstress}
J.~I. Hidalgo, R.~Fern{\'{a}}ndez, J.~M. Colmenar, F.~Cioffi, J.~L.
  Risco{-}Mart{\'{\i}}n, G.~Gonz{\'{a}}lez{-}Doncel, Using evolutionary
  algorithms to determine the residual stress profile across welds of
  age-hardenable aluminum alloys, Appl. Soft Comput. 40 (2016) 429--438.
\textcolor{blue}{
\bibitem{KAUR2018183}
M.~Kaur, S.~Kadam, A novel multi-objective bacteria foraging optimization
  algorithm ({MOBFOA}) for multi-objective scheduling, Appl. Soft Comput. 66
  (2018) 183 -- 195.
}
\textcolor{blue}{
\bibitem{XU2018268}
Y.~Xu, O.~Ding, R.~Qu, K.~Li, Hybrid multi-objective evolutionary algorithms
  based on decomposition for wireless sensor network coverage optimization,
  Appl. Soft Comput. 68 (2018) 268 -- 282.
}

\bibitem{DBLP:series/ncs/EibenS15}
A.~E. Eiben, J.~E. Smith, Introduction to Evolutionary Computing, Natural
  Computing Series, Springer, 2015.

\bibitem{TalbiUnified2018}
E.-G. Talbi,
  \href{https://www.sciencedirect.com/science/article/pii/S074373151830279X}{A
  unified view of parallel multi-objective evolutionary algorithms}, J.
  Parallel Distrib. Comput. (2018) --In press.

\bibitem{Dorronsoro13superlinear}
B.~Dorronsoro, G.~Danoy, A.~J. Nebro, P.~Bouvry, Achieving super-linear
  performance in parallel multi-objective evolutionary algorithms by means of
  cooperative coevolution, Computers {\&} {OR} 40~(6) (2013) 1552--1563.

\bibitem{Deb00NSGAII}
K.~Deb, S.~Agrawal, A.~Pratap, T.~Meyarivan, A fast elitist non-dominated
  sorting genetic algorithm for multi-objective optimisation: {NSGA-II}, in:
  M.~Schoenauer, K.~Deb, G.~Rudolph, X.~Yao, E.~Lutton, J.~J.~M. Guerv{\'{o}}s,
  H.~Schwefel (Eds.), Parallel Problem Solving from Nature - {PPSN} VI, 6th
  International Conference, Paris, France, September 18-20, 2000, Proceedings,
  Vol. 1917 of Lecture Notes in Computer Science, Springer, 2000, pp. 849--858.

\bibitem{Alba13parallel}
E.~Alba, G.~Luque, S.~Nesmachnow, Parallel metaheuristics: recent advances and
  new trends, Int. T. Oper. Res. 20~(1) (2013) 1--48.

\bibitem{Folino03cellular}
G.~Folino, C.~Pizzuti, G.~Spezzano, A scalable cellular implementation of
  parallel genetic programming, {IEEE} Trans. Evolutionary Computation 7~(1)
  (2003) 37--53.

\bibitem{Branke04Parallelizingcone}
J.~Branke, H.~Schmeck, K.~Deb, R.~S. Maheshwar, Parallelizing multi-objective
  evolutionary algorithms: cone separation, in: Proceedings of the {IEEE}
  Congress on Evolutionary Computation, {CEC} 2004, 19-23 June 2004, Portland,
  OR, {USA}, {IEEE}, 2004, pp. 1952--1957.

\bibitem{Zhang17DECAL}
Y.~H. Zhang, Y.~J. Gong, T.~L. Gu, H.~Q. Yuan, W.~Zhang, S.~Kwong, J.~Zhang,
  Decal: Decomposition-based coevolutionary algorithm for many-objective
  optimization, IEEE T. Cybernetics (2017) 1--15.

\bibitem{Tonda12cooperative}
A.~P. Tonda, E.~Lutton, G.~Squillero, A benchmark for cooperative coevolution,
  Memet. Comput. 4~(4) (2012) 263--277.

\bibitem{Kimovski15Parallel}
D.~Kimovski, J.~Ortega, A.~Ortiz, R.~Ba{\~{n}}os, Parallel alternatives for
  evolutionary multi-objective optimization in unsupervised feature selection,
  Expert Syst. Appl. 42~(9) (2015) 4239--4252.

\bibitem{Jia19Coevo}
Y.~Jia, W.~Chen, T.~Gu, H.~Zhang, H.~Yuan, S.~Kwong, J.~Zhang,
  Distributed cooperative
  co-evolution with adaptive computing resource allocation for large scale
  optimization, {IEEE} Trans. Evolutionary Computation 23~(2) (2019) 188--202.

\bibitem{Garcia16hpmoon}
P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~Ortega, J.~Gonz{\'{a}}lez, P.~A. Castillo,
  J.~J. Merelo, Addressing high dimensional multi-objective optimization
  problems by coevolutionary islands with overlapping search spaces, in:
  G.~Squillero, P.~Burelli (Eds.), Applications of Evolutionary Computation -
  19th European Conference, EvoApplications 2016, Porto, Portugal, March 30 -
  April 1, 2016, Proceedings, Part {II}, Vol. 9598 of Lecture Notes in Computer
  Science, Springer, 2016, pp. 107--117.

\bibitem{Talbi08Parallel}
E.~Talbi, S.~Mostaghim, T.~Okabe, H.~Ishibuchi, G.~Rudolph, C.~A.~C. Coello,
  Parallel approaches for multiobjective optimization, in: J.~Branke, K.~Deb,
  K.~Miettinen, R.~Slowinski (Eds.), Multiobjective Optimization, Interactive
  and Evolutionary Approaches [outcome of Dagstuhl seminars]., Vol. 5252 of
  Lecture Notes in Computer Science, Springer, 2008, pp. 349--372.

\bibitem{Durillo08masterslave}
A.~J. Nebro, J.~J. Durillo, A study of the parallelization of the
  multi-objective metaheuristic {MOEA/D}, in: C.~Blum, R.~Battiti (Eds.),
  Learning and Intelligent Optimization, 4th International Conference, {LION}
  4, Venice, Italy, January 18-22, 2010. Selected Papers, Vol. 6073 of Lecture
  Notes in Computer Science, Springer, 2010, pp. 303--317.

\bibitem{Hiroyasu07discussion}
T.~Hiroyasu, K.~Yoshii, M.~Miki, Discussion of parallel model of
  multi-objective genetic algorithms on heterogeneous computational resources,
  in: H.~Lipson (Ed.), Genetic and Evolutionary Computation Conference, {GECCO}
  2007, Proceedings, London, England, UK, July 7-11, 2007, {ACM}, 2007, p. 904.

\bibitem{Deb03distributed}
K.~Deb, P.~Zope, A.~Jain, Distributed computing of {Pareto}-optimal solutions
  with evolutionary algorithms, in: C.~M. Fonseca, P.~J. Fleming, E.~Zitzler,
  K.~Deb, L.~Thiele (Eds.), Evolutionary Multi-Criterion Optimization, Second
  International Conference, {EMO} 2003, Faro, Portugal, April 8-11, 2003,
  Proceedings, Vol. 2632 of Lecture Notes in Computer Science, Springer, 2003,
  pp. 534--549.

\bibitem{Wang09parallel}
W.~Zhi-xin, G.~Ju, A parallel genetic algorithm in multi-objective
  optimization, in: Control and Decision Conference, 2009. CCDC '09. Chinese,
  2009, pp. 3497--3501.

\bibitem{Xiao03specialized}
N.~Xiao, M.~P. Armstrong, A specialized island model and its application in
  multiobjective optimization, in: E.~Cant{\'{u}}{-}Paz, J.~A. Foster, K.~Deb,
  L.~Davis, R.~Roy, U.~O'Reilly, H.~Beyer, R.~K. Standish, G.~Kendall, S.~W.
  Wilson, M.~Harman, J.~Wegener, D.~Dasgupta, M.~A. Potter, A.~C. Schultz,
  K.~A. Dowsland, N.~Jonoska, J.~F. Miller (Eds.), Genetic and Evolutionary
  Computation - {GECCO} 2003, Genetic and Evolutionary Computation Conference,
  Chicago, IL, USA, July 12-16, 2003. Proceedings, Part {II}, Vol. 2724 of
  Lecture Notes in Computer Science, Springer, 2003, pp. 1530--1540.

\bibitem{Martens13asynchronous}
M.~M{\"{a}}rtens, D.~Izzo, The asynchronous island model and {NSGA-II:} study
  of a new migration operator and its performance, in: C.~Blum, E.~Alba (Eds.),
  Genetic and Evolutionary Computation Conference, {GECCO} '13, Amsterdam, The
  Netherlands, July 6-10, 2013, {ACM}, 2013, pp. 1173--1180.
\textcolor{blue}{\bibitem{DorronsoroPSO2018}
A.~Atashpendar, B.~Dorronsoro, G.~Danoy, P.~Bouvry, A scalable parallel
  cooperative coevolutionary {PSO} algorithm for multi-objective optimization,
  J. Parallel Distrib. Comput. 112 (2018) 111--125.
}

\bibitem{CaoZLL17}
B.~Cao, J.~Zhao, Z.~Lv, X.~Liu, A distributed parallel cooperative
  coevolutionary multiobjective evolutionary algorithm for large-scale
  optimization, {IEEE} T. Ind. Inform. 13~(4) (2017) 2030--2038.

\bibitem{cheng2015adaptive}
R.~Cheng, Y.~Jin, K.~Narukawa, Adaptive reference vector generation for inverse
  model based evolutionary multiobjective optimization with degenerate and
  disconnected {Pareto} fronts, in: Evolutionary Multi-Criterion Optimization,
  Springer International Publishing, 2015, pp. 127--140.

\bibitem{LUO2017235}
J.~Luo, Q.~Liu, Y.~Yang, X.~Li, M.~rong Chen, W.~Cao, An artificial bee colony
  algorithm for multi-objective optimisation, Appl. Soft Comput. 50 (2017) 235
  -- 251.
\textcolor{blue}{
\bibitem{Keratmatpour2018Taguchi}
M.~Keramatpour, S.~T.~A. Niaki, S.~H.~R. Pasandideh, A bi-objective two-level
  newsvendor problem with discount policies and budget constraint, Comput. Ind.
  Eng. 120 (2018) 192 -- 205.
}

\bibitem{zdt2000a}
E.~Zitzler, K.~Deb, L.~Thiele, {Comparison of Multiobjective Evolutionary
  Algorithms: Empirical Results}, Evol. Comput. 8~(2) (2000) 173--195.

\bibitem{EVALUATIONPARALLEL}
E.~Alba, G.~Luque, Evaluation of parallel metaheuristics, in: L.~Paquete,
  M.~Chiarandini, D.~Basso (Eds.), Empirical Methods for the Analysis of
  Algorithms, Workshop EMAA 2006, Proceedings, Reykjavik, Iceland, 2006, pp.
  9--14.

\bibitem{cantu1998survey}
E.~Cant{\'u}-Paz, A survey of parallel genetic algorithms, Calculateurs
  paralleles, reseaux et systems repartis 10~(2) (1998) 141--171.

\bibitem{xiong2003parallel}
S.~Xiong, F.~Li, Parallel strength {Pareto} multi-objective evolutionary
  algorithm for optimization problems, in: Evolutionary Computation, 2003.
  CEC'03. The 2003 Congress on, Vol.~4, IEEE, 2003, pp. 2712--2718.

\bibitem{ECJ}
S.~Luke, et~al., {ECJ: A Java-based Evolutionary Computation and Genetic
  Programming Research System}, available at
  \url{http://www.cs.umd.edu/projects/plus/ec/ecj} (2009).

\bibitem{Durillo11Jmetal}
J.~J. Durillo, A.~J. Nebro, jmetal: {A} java framework for multi-objective
  optimization, Adv. Eng. Softw. 42~(10) (2011) 760--771.
\textcolor{blue}{
\bibitem{Li17read}
M.~Li, L.~Zhen, X.~Yao, How to read many-objective solution sets in parallel
  coordinates [educational forum], {IEEE} Comp. Int. Mag. 12~(4) (2017)
  88--100.
}
\end{thebibliography}
